Crystals

### 2017-01-26 doc/ms.tex
Crystallinity
A bit of writing about the shape of the model curve

\documentclass[a4paper, 12pt]{article}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[left=2cm, right=2cm, bottom=3cm, top=2cm]{geometry}
\usepackage{natbib}
\usepackage{microtype}

\newcommand{\hypers}{\boldsymbol{\alpha}}
\newcommand{\params}{\boldsymbol{\theta}}
\newcommand{\data}{\boldsymbol{x}}
\newcommand{\info}{\boldsymbol{M}}

@@

@@

>>>>

\documentclass[a4paper, 12pt]{article}
\usepackage{amsmath}
\usepackage{color}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[left=2cm, right=2cm, bottom=3cm, top=2cm]{geometry}
\usepackage{natbib}
\usepackage{microtype}

\definecolor{orange}{rgb}{1, 0.5, 0}
\definecolor{green}{rgb}{0, 0.5, 0}

\newcommand{\hypers}{\boldsymbol{\alpha}}
\newcommand{\params}{\boldsymbol{\theta}}
\newcommand{\data}{\boldsymbol{x}}
\newcommand{\info}{\boldsymbol{M}}
\newcommand{\x}{x}
\newcommand{\todo}{\color{orange} \bf}

@@

\subsection{The shape of the model curve}
The function $f(\x)$, defined from $\x_{\rm min}$ to $\x_{\rm max}$,
is assumed to be a sum of the following components:
\begin{enumerate}
\item A background component
\item $N_{\rm wide}$ wide gaussians
\item $N_{\rm narrow}$ narrow gaussians, to model the spikes
\end{enumerate}

The background component is assumed to be linear
{\todo between $x_{\rm min}$ and A, between A and B, and between B
and $x_{\rm max}$}.

\subsection{Prior probability distributions}

@@

The shape of the model function $f(x)$ is therefore
\begin{align}
f(x) &= A + f_{\rm wide}(x) + \sum_{i=1}^N a_i f_i(x)
\end{align}
and the crystallinity is
\begin{align}
C &= \frac{\int f_{\rm wide}(x) \, dx}
          {\int f_{\rm wide}(x) \, dx + \int f_{\rm narrow}(x) \, dx}
\end{align}
